An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
Update main.tex

	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance. Similar to the selectivity observed in attribute filtering. }
	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors. With a smaller range, fewer points remain after filtering, resulting in lower computational cost. In addition, the performance of Faiss is influenced by data dimensionality; \textcolor{blue}{ the higher the dimensionality, the worse the performance.}

>>>>

	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance. Similar to the selectivity observed in attribute filtering. }
	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors. With a smaller range, fewer points remain after filtering, resulting in lower computational cost. In addition, the performance of Faiss is influenced by data dimensionality; \textcolor{blue}{ the higher the dimensionality, the worse the performance.}
